\bf Supervised Tensor Decomposition with Interactive Side Information

### 2021-06-21 tensor_regress/JCGS/jcgs_submission/jcgs-tensor.tex
clean

\if0\blind
{
  \title{\bf Supervised Tensor Decomposition with Interactive Side Information}
  \author{Jiaxin Hu, Zhuoyan Xu, Chanwoo Lee, and Miaoyan Wang\thanks{The authors gratefully acknowledge NSF grant DMS-1915978 and funding from the Wisconsin Alumni Research Foundation. }\hspace{.2cm}\\
    Department of Statistics, University of Wisconsin-Madison}
  \maketitle

>>>>

\if0\blind
{
  \title{\bf Supervised Tensor Decomposition with Interactive Side Information}
  \author{Jiaxin Hu, Chanwoo Lee, and Miaoyan Wang\thanks{The authors gratefully acknowledge NSF grant DMS-1915978 and funding from the Wisconsin Alumni Research Foundation. }\hspace{.2cm}\\
    Department of Statistics, University of Wisconsin-Madison}
  \maketitle
